---
title: "GC_AMPK"
author: "LH"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,dev = "pdf",fig.path = "./pdf/",out.height = "450px",warning = F)
```


```{r working directory}
working_directory = "~/r_workspace/practice/gc_redo//" # working directory

setwd(working_directory)

```



```{r source}

source("~/r_workspace/script/rscript/fun_source_dir.R")

# pkgs
suppressMessages(
  {
    require(DT)
    require(survcomp)
    require(survminer)
      require(factoextra)
  require(FactoMineR)
  }
)

fun_source_dir("~/r_workspace/script/rscript/")
source("./src/src.R")

```


```{r data_structure}
# 1) all your data ds

ds_list = list()

ds_list$tcga = readRDS("data/stad_ampk.rds")

ds_list$tcga $clin %<>% 
  mutate(AMPK_score = AMPK_score) %>% 
  select(-AMPK_score)

# 2) all your clin list
clin_list = list()

# 3) all your annotation list: data.frame, rownames is accession
anno_list = list()

# 4) config_list: all the other list
config_list = list()

# 5) maf list
maf_list = list()

# 6) data others
others_list = list()


# 7) results list
results_list = list()


# 8) genes list
genes_list = list()



```


```{r project_data}
# write you r project data here
others_list$ampk_genes = fread("../GC_cluster_ampk/Figs_V2/table_1_AMPK_genesList.csv")

others_list$ampk_genes %>% 
  select(-V1) %>% 
  fun_dt_dt(x_name = "ampk_genes_list")


# palette
palette = "lancet"

pfs_lable = c("Progress Free Survival (Months)","Progression Free Status","1:PROGRESSION")

dss_label =  c("Months of disease-specific survival","Disease-specific Survival status","1:DEAD WITH TUMOR")

# theme
theme_now = function(...){
  theme_clean()+
    theme(
      plot.background = element_blank(),
      panel.background = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      legend.background = element_blank(),
      legend.title = element_text(size = 9,face = "plain"),
      legend.text = element_text(size = 9,face = "plain"),
      legend.position = "top",
      axis.text = element_text(size = 9),
      axis.title = element_text(size = 12),
      plot.title = element_text(size = 14),
      panel.grid.major.y = element_blank()
    )+
    theme(...)
}


func.pca.signature = function(input.expr,feature.selected){
  # get signature 1 -----
  pca.sig1 = PCA(t(na.omit(input.expr[match(feature.selected$genes$up,rownames(input.expr)),])),graph = F)
  pca.sig1.df = data.frame(pca.sig1$ind$coord[,1])
  colnames(pca.sig1.df) = "Signature_1"
  # get signature 2 -----
  pca.sig2 = PCA(t(na.omit(input.expr[match(feature.selected$genes$down,rownames(input.expr)),])),graph = F)
  pca.sig2.df =  data.frame(pca.sig2$ind$coord[,1])
  colnames(pca.sig2.df) = "Signature_2"
  
  
  # get score----------
  pca.sig.score = merge(pca.sig1.df,pca.sig2.df,by=0)
  pca.sig.score$AMPK_score = pca.sig.score$Signature_1  - pca.sig.score$Signature_2
  return(pca.sig.score)
}

```

# consensus clustering analysis

```{r}
tcga.stad.expr.matr.genes = na.omit(tcga.stad.expr.matr[match(genes.table$hs_ens,rownames(tcga.stad.expr.matr)),])

csc.cluster1 = ConsensusClusterPlus(d=tcga.stad.expr.matr.genes
                                        ,maxK =7
                                        ,reps = 1000
                                        ,pItem = 0.8
                                        ,pFeature = 1
                                        ,clusterAlg="km"
                                        ,distance="euclidean"
                                        ,seed=12321
                                        ,title = "E://file/GC_AMPK/r_data/concensusClusterFigures"
                                        ,plot="png")
  
# cluster
optimal.k.value = optimal.k(csc.cluster1,5)
csc.cluster = data.frame(csc.cluster1[[optimal.k.value]]$consensusClass)
colnames(csc.cluster) = "Cluster"
table(csc.cluster$Cluster)
tcga.stad.clin$Cluster =  csc.cluster$Cluster[match(tcga.stad.clin$`Sample ID`,rownames(csc.cluster))]

```

# cluster heatmap


```{r}
# cluster annotation
cls.anno = na.omit(data.frame(row.names = tcga.stad.clin$`Sample ID`,
                     Cluster = factor(tcga.stad.clin$Cluster)))
cls.anno = cls.anno[order(cls.anno$Cluster),,drop=F]
# heatmap annotation for MAPK gense
hm.anno = data.frame(row.names = tcga.stad.clin$`Sample ID`,
                     Cluster = factor(tcga.stad.clin$Cluster))
hm.anno = hm.anno[order(hm.anno$Cluster),,drop=F]
hm.anno = hm.anno[intersect(rownames(hm.anno),colnames(tcga.stad.expr.matr.genes.zscore)),,drop=F]
hm.anno$T_stage = tcga.clin$T_stage[match(rownames(hm.anno),tcga.clin$`Sample ID`)]
hm.anno$N_stage = tcga.clin$N_stage[match(rownames(hm.anno),tcga.clin$`Sample ID`)]
hm.anno$M_stage = tcga.clin$M_stage[match(rownames(hm.anno),tcga.clin$`Sample ID`)]
hm.anno$Histological_grade = tcga.clin$Neoplasm_Histologic_Grade[match(rownames(hm.anno),tcga.clin$`Sample ID`)]
hm.anno$Disease_stage = tcga.clin$Neoplasm_Disease_Stage[match(rownames(hm.anno),tcga.clin$`Sample ID`)]
# fisher test
hm.anno %>% 
  {table(.$Cluster,.$T_stage)} %>% 
  fisher.test() %>% 
  .$p.value %>% 
  gtools::stars.pval()
hm.anno %>% 
  {table(.$Cluster,.$N_stage)} %>% 
  fisher.test() %>% 
  .$p.value %>% 
  gtools::stars.pval()
hm.anno %>% 
  {table(.$Cluster,.$M_stage)} %>% 
  fisher.test() %>% 
  .$p.value %>% 
  gtools::stars.pval()
hm.anno %>% 
  {table(.$Cluster,.$Disease_stage)} %>% 
  fisher.test() %>% 
  .$p.value %>% 
  gtools::stars.pval()
hm.anno %>% 
  {table(.$Cluster,.$Histological_grade)} %>% 
  fisher.test() %>% 
  .$p.value %>% 
  gtools::stars.pval()


table(hm.anno$Cluster)
pheatmap(tcga.stad.expr.matr.genes.zscore[,rownames(hm.anno)],
         show_rownames = F,
         show_colnames = F,
         cluster_cols = F,
         annotation_col = hm.anno,
         annotation_colors  = list(Cluster=c(`1`="#174889",`2`="#ec1d25"),
                                   T_stage = c(T1 = "#83EADD",T2 = "#3BD1BF",T3 = "#0DA391",T4 = "#07544B"),
                                   N_stage = c(N0 = "#E5EA83",N1 = "#DAE055",N2 = "#C9D124",N3 = "#A6AD21"),
                                   M_stage = c(M0 = "#AA7FC6",M1 = "#773E9B"),
                                   Histological_grade = c(G1 = "#75DB92",G2 = "#36C960",G3 = "#197032"),
                                   Disease_stage = c('STAGE I' = "#83EADD",'STAGE II' = "#3BD1BF",'STAGE III' = "#0DA391","STAGE IV" = "#07544B")))


```

# cluster enrichment

```{r}
cluster_deg_enrichment_kegg = enrichKEGG(input.gene.table$ENTREZID[match(deg.hs,input.gene.table$SYMBOL)])
#cluster_deg_enrichment_kegg = setReadable(cluster_deg_enrichment_kegg,OrgDb = org.Hs.eg.db,keyType = "ENTREZID")
fc = structure(tcga.cls.deg$logFC,names = tcga.cls.deg$ID)

cnetplot(cluster_deg_enrichment_kegg,circular = TRUE, colorEdge = TRUE,
         foldChange = fc,cex_label_gene  = 0.2,
         node_label = "gene",
         showCategory = c("Calcium signaling pathway",
                          "ECM-receptor interaction",
                          "cAMP signaling pathway",
                          "Cell adhesion molecules",
                          "PI3K-Akt signaling pathway"))

```


# cluster pca analysis

```{r}
pca.res = PCA(t(tcga.stad.expr.matr.genes),graph = F)
tcga.mapk.pca.plot = fviz_pca_ind(pca.res,label=F,habillage = cls.anno[colnames(tcga.stad.expr.matr.genes),],addEllipses = T)

```


# cluster differential expression analysis

```{r}
# 5. Cluster Deg-------------
# deg data preprocess
func.deg.data.pre = function(input.expr.matr,remove.zeros.pct = 0.2){
  require(clusterProfiler)
  require(org.Hs.eg.db)
  input.gene.table <<- bitr(rownames(input.expr.matr),fromType = 'SYMBOL',toType = "ENTREZID",OrgDb = org.Hs.eg.db)
  input.expr.matr = input.expr.matr[input.gene.table$SYMBOL,]
  # remove zeros
  if(!is.null(remove.zeros.pct)){
    z_value = min(input.expr.matr)
    z_count = ncol(input.expr.matr) * remove.zeros.pct
    input.expr.matr = input.expr.matr[rowSums(input.expr.matr == z_value) < z_count,]
    
  }
  return(input.expr.matr)
  
}
tcga.stad.expr.matr.pre = func.deg.data.pre(tcga.stad.expr.matr)
# DEG analysis here 
tcga.cls.deg = DegLimmaFunc(tcga.stad.expr.matr.pre,anno = cls.anno,contrast = c(2,1))
# reorder deg list
tcga.cls.deg = tcga.cls.deg[order(tcga.cls.deg$logFC),]
# gene up regulated
sum(tcga.cls.deg$logFC > 1 & tcga.cls.deg$adj.P.Val < 0.01)
# gene down regulateds
sum(tcga.cls.deg$logFC < -1 & tcga.cls.deg$adj.P.Val < 0.01)
deg.hs = tcga.cls.deg$ID[tcga.cls.deg$adj.P.Val<0.01 & abs(tcga.cls.deg$logFC) > 1]
length(deg.hs)

tcga.cls.deg$Regulation = ifelse(tcga.cls.deg$adj.P.Val > 0.01 | abs(tcga.cls.deg$logFC ) < 1,"notSig",
                              ifelse(tcga.cls.deg$logFC > 0 ,"up","down")) 

table(tcga.cls.deg$Regulation)
# Figures 1, volcano
tcga.cls.deg %>%
  ggplot() +
  geom_point(aes(logFC,-log10(adj.P.Val),color = Regulation)) +
  scale_color_manual(values = c("#174889","gray","#ec1d25"))


pheatmap(as.matrix(tcga.stad.expr.zscore.matr[deg.hs,sampleid.hm.tmp]),
         show_rownames = F,
         show_colnames = F,
         cluster_cols = F,
         cluster_rows = F,
         annotation_col = cls.anno[intersect(rownames(cls.anno),colnames(tcga.stad.expr.zscore.matr)),,drop=F],
         annotation_colors  = list(Cluster=c(`1`="#174889",`2`="#ec1d25")))



```



# featue selection by rf

```{r}

# 6. Feature selection------------------
func.feature.boruta.deg = function(input.deg,input.expr,input.cluster){
  # megrge exprssion data and cluster
  input.expr.df = data.frame(t(input.expr),check.names = F)
  input.expr.df$Cluster = input.cluster[[1]][match(rownames(input.expr.df),rownames(input.cluster))]
  
  # 1. up
  deg.up = input.deg$ID[input.deg$adj.P.Val < 0.01 & input.deg$logFC > 1]
  genes.keep.up = Boruta(Cluster~.,data = input.expr.df[,c(deg.up,'Cluster')])
  genes.keep.up.hs = names(genes.keep.up$finalDecision[genes.keep.up$finalDecision != 'Rejected'])
  # 2. down
  deg.down = input.deg$ID[input.deg$adj.P.Val < 0.01 & input.deg$logFC < -1]
  genes.keep.down = Boruta(Cluster~.,data = input.expr.df[,c(deg.down,'Cluster')])
  genes.keep.down.hs = names(genes.keep.down$finalDecision[genes.keep.down$finalDecision != 'Rejected'])
  
  return(list(res = list(genes.keep.up,genes.keep.down),
              genes = list(up = genes.keep.up.hs,
                           down = genes.keep.down.hs)))
}
# boruta
#feature.selected = func.feature.boruta.deg(tcga.cls.deg,tcga.stad.expr.matr.pre,cls.anno)
#feature.selected.copy= feature.selected
feature.selected$genes$up = gsub("\\`","",feature.selected$genes$up)
feature.selected$genes$down = gsub("\\`","",feature.selected$genes$down)

feature.selected.hs = unname(unlist(feature.selected$genes))
library(circlize)
col_fun = colorRamp2(c(-20, 0, 20), c("navy","white","firebrick3"))
ComplexHeatmap::Heatmap(as.matrix(tcga.stad.expr.matr[match(feature.selected.hs
                                                     ,rownames(tcga.stad.expr.matr))
                                               ,rownames(cls.anno)]),
         show_row_names  = F,
         show_column_names  = F,
         cluster_columns  = F,
         cluster_rows = F,
         top_annotation = ComplexHeatmap::HeatmapAnnotation(Cluster = cls.anno$Cluster,
                                                            col =  list(Cluster=c(`1`="#174889",`2`="#ec1d25"))),
         row_split = c(rep("Signature2",length(feature.selected$genes$up)),
                       rep("Signature1",length(feature.selected$genes$down))),
         row_km = T,
         column_split = cls.anno$Cluster,
         col = col_fun
         )

```


# signature construction function 

```{r}
func.pca.signature = function(input.expr,feature.selected){
  # get signature 1 -----
  pca.sig1 = PCA(t(na.omit(input.expr[match(feature.selected$genes$up,rownames(input.expr)),])),graph = F)
  pca.sig1.df = data.frame(pca.sig1$ind$coord[,1])
  colnames(pca.sig1.df) = "Signature_1"
  # get signature 2 -----
  pca.sig2 = PCA(t(na.omit(input.expr[match(feature.selected$genes$down,rownames(input.expr)),])),graph = F)
  pca.sig2.df =  data.frame(pca.sig2$ind$coord[,1])
  colnames(pca.sig2.df) = "Signature_2"
  
  
  # get score----------
  pca.sig.score = merge(pca.sig1.df,pca.sig2.df,by=0)
  pca.sig.score$AMPK_score = pca.sig.score$Signature_1  - pca.sig.score$Signature_2
  return(pca.sig.score)
}

```

# immune signature analysis: ESTIAMTE, CIBERSORT

```{r}

anno.group = data.frame(row.names = tcga.clin$`Sample ID`,
                        Group = tcga.clin$Group)

func.immue2(anno = na.omit(anno.group),palette = palette)
func.estimate2(anno = na.omit(anno.group),palette = palette,tcga.file = "~/r_workspace/db/tcga/estimate/STAD_rsem.txt")
```


# signature survival analysis

```{r }
ds_list$tcga$clin %>% 
  fun_surv_parsing("os") %>% 
  fun_surv_cutoff(feature = "AMPK_score") %>% 
  fun_surv_km(palette = palette,conf.int = F) %>% 
  fun_km_re(theme_now = theme_now())

ds_list$tcga$clin %>% 
  fun_surv_parsing("dfs") %>% 
  fun_surv_cutoff(feature = "AMPK_score") %>% 
  fun_surv_km(palette = palette,conf.int = F) %>% 
  fun_km_re(theme_now = theme_now())

ds_list$tcga$clin %>% 
  fun_surv_parsing(pfs_lable) %>% 
  fun_surv_cutoff(feature = "AMPK_score") %>% 
  fun_surv_km(palette = palette,conf.int = F) %>% 
  fun_km_re(theme_now = theme_now())

ds_list$tcga$clin %>% 
  fun_surv_parsing(dss_label) %>% 
  fun_surv_cutoff(feature = "AMPK_score") %>% 
  fun_surv_km(palette = palette,conf.int = F) %>% 
  fun_km_re(theme_now = theme_now())

```

# Signature enrichment

```{r}
# 16. signature correlation analysis------
harmark_enrichment = func.cor.enrichment(expr.matr = tcga.stad.expr.matr.pre,
                    score.dt = tcga.clin,score.id = "Sample ID",score.column = "Signature",enrichment = "hallmark")

ridgeplot(harmark_enrichment$hallmark,)

kegg_enrichment = func.cor.enrichment(expr.matr = tcga.stad.expr.matr.pre,
                                         score.dt = tcga.clin,score.id = "Sample ID",score.column = "Signature",enrichment = "kegg")
ridgeplot(kegg_enrichment$kegg,showCategory = 10)

```

# validation

```{r}

func.validation = function(gse.expr.list
                           ,feature.selected
                           ,gene.id.table=input.gene.table
                           ,sampleID = 'Sample ID'
                           ,os.label = c("time","status",1),
                           title=NULL){
  # parsing the gse data
  gse.expr = gse.expr.list$gse.expr
  gse.clin = gse.expr.list$gse.clin
  gse.expr[[1]] = input.gene.table$SYMBOL[match(gse.expr[[1]],input.gene.table$ENTREZID)]
  gse.expr = na.omit(gse.expr)
  input.expr = as.matrix(gse.expr[,-1])
  rownames(input.expr) = gse.expr$ENTREZID
  
  # 
  
  gse.ampk.score = func.pca.signature(input.expr,feature.selected)
  
  # merge data
  gse.clin$AMPK_score = gse.ampk.score$AMPK_score[match(gse.clin[[sampleID]],gse.ampk.score[[1]])]
  
  # survival----
  func.surv.dt(surv.dt =gse.clin,
               osOrdfs = os.label,
               survivalGroup = "AMPK_score",
               pct = 0.5,
               palette = palette,title = title)
  #return(gse.clin)
}

ggarrange(
func.validation(gse.expr.list = gse13861,feature.selected = feature.selected,title = "GSE13861")$plot,
func.validation(gse.expr.list = gse26901,feature.selected = feature.selected,title = "GSE26901")$plot,
func.validation(gse.expr.list = gse66229,feature.selected = feature.selected,title = "GSE66229")$plot,

func.validation(gse.expr.list = gse13861,feature.selected = feature.selected,os.label = c("RFS.m","Recurrence (1=yes, 0=no)",1),title = "GSE13861_RFS")$plot,


func.validation(gse.expr.list = gse26901,feature.selected = feature.selected,os.label = c("RFS.m","Recurrence (1=yes, 0=no)",1),title = "GSE26901_RFS")$plot,

func.validation(gse.expr.list = gse66229,feature.selected = feature.selected,c("DFS.m","Recur",1),title = "GSE66229_DFS")$plot,common.legend = T)


```

# clinical analysis

```{r}
ggarrange(plotlist = func.clin.line(input.clin = tcga.clin,features = c("T_stage","N_stage","M_stage","Neoplasm_Histologic_Grade"),rs = "Signature",palette = palette))
ggarrange(plotlist = func.clin.box(input.clin = tcga.clin,features = c("T_stage","N_stage","M_stage","Neoplasm_Histologic_Grade"),rs = "Signature",palette = palette))

```

# mutation analysis-mutation count

```{r}
maf = read.maf("~/r_workspace/db/tcga/tcga_stad/stad_tcga_pan_can_atlas_2018/data_mutations_mskcc.txt")
tcga.clin$Group = ifelse(tcga.clin$Signature > median(tcga.clin$Signature,na.rm = T),'High','Low')

signature_high_sampleID = na.omit(tcga.clin$`Sample ID`[tcga.clin$Group =="High"])
signature_low_sampleID = na.omit(tcga.clin$`Sample ID`[tcga.clin$Group =="Low"])

maf_high = subsetMaf(maf,tsb = signature_high_sampleID)
maf_low = subsetMaf(maf,tsb = signature_low_sampleID)
oncoplot(maf_high)
oncoplot(maf_low)
maf_compare_df = mafCompare(maf_high,maf_low,m1Name = "Signature_high",m2Name =  "Signature_low")
maf_compare_df$results = maf_compare_df$results[(maf_compare_df$results$Signature_high + maf_compare_df$results$Signature_low)>50,]

maf_compare_df$results = maf_compare_df$results[order(maf_compare_df$results$Signature_high,decreasing = T),]
forestPlot(maf_compare_df,pVal = 0.01)

ggboxplot(tcga.clin,x="Group")

tcga.clin %>% 
  filter(!is.na(Group)) %>% 
  ggplot(aes(x = Group, y = Mutation_count)) +
  geom_violin(aes(fill = Group)) +
  geom_boxplot(width = 0.2) +
  scale_y_log10() +
  stat_compare_means()

lollipopPlot2(maf_high,maf_low,m1_name = "Signature high",m2_name = "Signature low",gene = 'TTN')
lollipopPlot2(maf_high,maf_low,m1_name = "Signature high",m2_name = "Signature low",gene = 'MUC16')
lollipopPlot2(maf_high,maf_low,m1_name = "Signature high",m2_name = "Signature low",gene = 'LRP1B')

```



# stad analysis

```{r}

# 14. imvigor effects has benefits, DO TIDE, T-cell exclusions, TIDE score----
tcga.stad.expr.matr.pre.nor = t(apply(tcga.stad.expr.matr.pre,1,function(x)(x - mean(x))))
write.table(tcga.stad.expr.matr.pre.nor,file = "stad.txt",row.names = T,col.names = T,sep = "\t")
stad_tide = fread("stad_tide.csv")
stad_tide$Group = tcga.clin$Group[match(stad_tide$Patient,tcga.clin$`Sample ID`)]
table(stad_tide$Group)
colnames(stad_tide)
ggarrange(ggboxplot(stad_tide,x="Group",y="TIDE",fill="Group",palette = palette) + stat_compare_means(),
ggboxplot(stad_tide,x="Group",y="Dysfunction",fill="Group",palette = palette) + stat_compare_means(),
ggboxplot(stad_tide,x="Group",y="Exclusion",fill="Group",palette = palette) + stat_compare_means(),
nrow = 1,ncol = 3,common.legend = T)
ggplot(data = stad_tide) +
  geom_bar(aes(x=Group,fill=Responder),position = "fill")+fill_palette(palette = palette) +
  annotate("text",x = 1.5, y = 1.03,label= 'p=1e-07')
fisher.test(table(stad_tide$Group,stad_tide$Responder ))

ggboxplot(stad_tide,x="Group",y="CD8") + stat_compare_means()
ggboxplot(stad_tide,x="Group",y="caf") + stat_compare_means()
# part3: subtypes
tcga_subtypes = na.omit(data.frame(row.names = tcga.clin$`Sample ID`,
                           Cluster = factor(tcga.clin$Cluster),
                           Subtypes = tcga.clin$`Cancer Type Detailed`))

ggplot(data = tcga_subtypes) +
  geom_bar(aes(x=Cluster,fill=Subtypes),position = "fill") + theme_classic2()
fisher.test(as.matrix(table(tcga_subtypes$Cluster,tcga_subtypes$Subtypes)),hybrid = T)

```

# imvigor analysis
```{r }

func.imvigor = function(model.coef,palette = "simpsons"){
  library(IMvigor210CoreBiologies)
  require(ggpubr)
  require(pROC)
  data(cds)
  cds2 <- cds
  voomD <- filterNvoom(counts(cds2),
                       minSamples=ncol(counts(cds2))/10,
                       minCpm=0.25)
  m <- voomD$E
  m <- t(scale( t( m ),
                center=TRUE, 
                scale=TRUE)
  )
  feature.df = cds@featureData@data
  imvi.expr =m
  # rename the epxressio data with hugo symbol
  rownames(imvi.expr) = feature.df$symbol[match(rownames(imvi.expr),feature.df$entrez_id)]

  # get clinical data
  imvigor.clin = fread("~/r_workspace/db/gse/imvigor210/imvigor_clin.csv")
  
  # merge the clinical data
  imvigor.clin = func.pca.signature(input_expr = imvi.expr,
                                    sig_1 = feature.selected$genes$up,
                                    sig_2 = feature.selected$genes$down,
                                    tcga.clin = imvigor.clin,SampleID = "V1",
                                    Surv_p = F)
  # survival analysis----
  km = func.surv.dt(surv.dt = imvigor.clin
                    ,osOrdfs = c("os","censOS",1)
                    ,survivalGroup = 'Risk_score'
                    ,pct = 0.69
                    ,title = "Imvigor210 Overall survival KM"
                    ,palette = palette )
  # ggboxplot
  box.plot = ggboxplot(imvigor.clin[!is.na(imvigor.clin$binaryResponse),]
                       ,x="binaryResponse"
                       ,y="Risk_score"
                       ,fill = "binaryResponse"
                       ,palette = palette) + 
    stat_compare_means()
  
  # pROC
  roc.res = roc(response = imvigor.clin$binaryResponse,
                predictor = imvigor.clin$Risk_score
                ,auc = T)
  plot.roc(roc.res,add=F, xlim = c(1,0),ylim=c(0,1),print.auc = T,plot=F)
  
  return(list(
     clin = imvigor.clin,
    km=km,
    boxplot = box.plot,
    roc=roc.res
  ))
}

imvigor_list = func.imvigor(1,palette = palette ) # 1 is not used 
imvigor_list$clin$Group = ifelse(imvigor_list$clin$Risk_score > quantile(imvigor_list$clin$Risk_score,0.69),"High","Low")

imvi_fisher = fisher.test(imvigor_list$clin$Group,imvigor.clin$binaryResponse)
imvigor_list$clin %>% 
  filter(!is.na(binaryResponse)) %>% 
  ggplot(aes(x = Group, fill = binaryResponse)) + 
  geom_bar(position = "fill") +
  annotate("text",x = 1.5, y = 1.03,label = paste0("p=",round(imvi_fisher$p.value,3))) +
  fill_palette(palette = palette)

```



# ic50 analysis

```{r}

tcga.clin_ic50_func = drug.pred.func(tcga.expr.matr = tcga.stad.expr.matr.pre,drugs = drugs_list,
                                      tcga.clin = tcga.clin)


tcga.clin_ic50_func %>% 
  filter(!is.na(Group)) %>% 
  select(one_of(c("Group",drugs_list))) %>% 
  melt() %>% 
  group_by(variable) %>% 
  do(t_test = t.test(.$value[.$Group == "Low"],
                     .$value[.$Group == "High"])) %>% 
  mutate(pvalue = t_test$p.value) %>% 
  mutate(p.adj = p.adjust(p = pvalue,method = "fdr",n=length(drugs_list))) %>% 
  filter(pvalue < 0.05) %>% 
  .[[1]] %>% 
  as.character() -> drugs

drugs = c("Cisplatin","Axitinib","Docetaxel","Mitomycin.C","Bortezomib","Paclitaxel","Sorafenib")

plot_function = function(x){
  ggplot(tcga.clin_ic50_func[!is.na(Group),],aes_string(x = "Group", y = x,fill = "Group"))+
    geom_violin() +geom_boxplot(width = 0.2) +
    stat_compare_means(label = "p.signif",label.x = 1.4)+
    theme(axis.title.x = element_blank()) +
    fill_palette(palette = palette)
}

ggarrange(plotlist = drugs %>% 
            map(plot_function),
          common.legend = T,nrow=2,ncol = 4)

```


# signature subtype analysis

```{r}

tcga.clin %>% 
  dplyr::filter(!is.na(Subtype)) %>% 
  count(Group,Subtype)

tcga.clin %>% 
  dplyr::filter(!is.na(Subtype)) %>% 
  count(Group,Subtype) %>%
  ggplot(aes(y = n,axis2 = Group,axis1 = Subtype)) +
  geom_alluvium(aes(fill = Subtype))+
  scale_x_discrete(limits = c("Subtype", "Signature"), expand = c(.2, .05)) +
  #xlab(gene) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  theme_minimal() +
  fill_palette(palette = palette)


# subtype stratification

tcga.clin %>% 
  filter(!is.na(Subtype) &Subtype != 'STAD_GS') %>% 
  func.surv.dt(osOrdfs = "os",survivalGroup = "Group",palette = palette)
tcga.clin %>% 
  filter(!is.na(Subtype) &Subtype != 'STAD_GS') %>% 
  func.surv.dt(osOrdfs = "dfs",survivalGroup = "Group",palette = palette)
tcga.clin %>% 
  filter(!is.na(Subtype) &Subtype != 'STAD_GS') %>% 
  func.surv.dt(osOrdfs = pfs_label,survivalGroup = "Group",palette = palette)
ggarrange(
tcga.clin %>% 
  filter(!is.na(Subtype) & !Subtype %in% c('STAD_GS',"STAD_MSI")) %>% 
  func.surv.dt(osOrdfs = "os",survivalGroup = "Signature",palette = palette,pct = seq(0.25,0.75,0.01),title = "OS") %>% .$plot,
tcga.clin %>% 
  filter(!is.na(Subtype) & !Subtype %in% c('STAD_GS',"STAD_MSI")) %>% 
  func.surv.dt(osOrdfs = "dfs",survivalGroup = "Signature",palette = palette,pct = seq(0.25,0.75,0.01),title = "DFS")%>% .$plot,

tcga.clin %>% 
  filter(!is.na(Subtype) & !Subtype %in% c('STAD_GS',"STAD_MSI")) %>% 
  func.surv.dt(osOrdfs = dds_label,survivalGroup = "Signature",palette = palette,pct = seq(0.25,0.75,0.01),title = "DSS")%>% .$plot,


tcga.clin %>% 
  filter(!is.na(Subtype) & !Subtype %in% c('STAD_GS',"STAD_MSI")) %>% 
  func.surv.dt(osOrdfs = pfs_label,survivalGroup = "Signature",palette = palette,pct = seq(0.25,0.75,0.01),title = "PFS")%>% .$plot,
common.legend = T,nrow = 1,ncol = 4)

tcga.clin %>% 
  filter(!is.na(Subtype) & !is.na(Group)) %>% 
  mutate(GS_Signature = ifelse(Subtype == "STAD_GS","GS","Others")) %>% 
  mutate(GS_Signature = paste(GS_Signature,Group,sep = "_"))  %>% 
  func.surv.dt(osOrdfs = "os",survivalGroup = "GS_Signature",palette = palette)
tcga.clin %>% 
  filter(!is.na(Subtype) & !is.na(Group)) %>% 
  mutate(GS_Signature = ifelse(Subtype == "STAD_GS","GS","Others")) %>% 
  mutate(GS_Signature = paste(GS_Signature,Group,sep = "_"))  %>% 
  func.surv.dt(osOrdfs = "dfs",survivalGroup = "GS_Signature",palette = palette)


tcga.clin %>% 
  filter(!is.na(Subtype) & !is.na(Group)) %>% 
  mutate(GS_Signature = ifelse(Subtype == "STAD_GS","GS","Others")) %>% 
  mutate(GS_Signature = paste(GS_Signature,Group,sep = "_"))  %>% 
  func.surv.dt(osOrdfs = dds_label,survivalGroup = "GS_Signature",palette = palette)


tcga.clin %>% 
  filter(!is.na(Subtype) & !is.na(Group)) %>% 
  mutate(GS_Signature = ifelse(Subtype == "STAD_GS","GS","Others")) %>% 
  mutate(GS_Signature = paste(GS_Signature,Group,sep = "_"))  %>% 
  func.surv.dt(osOrdfs = pfs_label,survivalGroup = "GS_Signature",palette = palette)



gse66229_clin %>% 
  mutate(ACRG.sub = factor(ACRG.sub,levels = c("EMT","TP53positive","TP53neg","MSI"))) %>% 
  ggplot(aes(x = ACRG.sub,y=MAPK_score,fill = ACRG.sub )) +
  geom_violin() +geom_boxplot(width = 0.2 ) +
  stat_compare_means(comparisons = list(c("EMT","TP53positive"),c("EMT","TP53neg"),c("EMT","MSI")))
    
gse66229_clin %>% 
  mutate(Group = ifelse(MAPK_score > median(MAPK_score),"High","Low")) %>% 
  dplyr::filter(!is.na(ACRG.sub)) %>% 
  count(Group,ACRG.sub) %>%
  ggplot(aes(y = n,axis2 = Group,axis1 = ACRG.sub)) +
  geom_alluvium(aes(fill = ACRG.sub))+
  scale_x_discrete(limits = c("Subtype", "Signature"), expand = c(.2, .05)) +
  #xlab(gene) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  theme_minimal() +
  fill_palette(palette = palette)

gse66229_clin %>% 
  mutate(Group = ifelse(MAPK_score > median(MAPK_score),"High","Low")) %>% 
  dplyr::filter(!is.na(ACRG.sub)) %>% 
  count(Group,ACRG.sub)

ggarrange(
gse66229_clin %>% 
  filter(ACRG.sub %in% c("TP53positive","TP53neg")) %>% 
  func.surv.dt(osOrdfs = c("DFS.m","Recur",1),
               survivalGroup = "MAPK_score",
               pct = seq(0.25,0.75,0.01),
               palette = palette,title = "TP53Postive&TP53negtive_DFS") %>% 
  .$plot,

gse66229_clin %>% 
  filter(ACRG.sub %in% c("TP53positive","TP53neg")) %>% 
  func.surv.dt(osOrdfs = NULL,
               survivalGroup = "MAPK_score",
               pct = seq(0.25,0.75,0.01),
               palette = palette,
               title = "TP53Postive&TP53negtive_OS") %>% 
  .$plot,common.legend = T)

```




# Add analysis in pancancer

```{r }
# get pan cancer data

pancancer.names = list.files("~/r_workspace/db/tcga/tcga_rds_v2/")

#load("../GC_cluster_ampk/.RData")
#saveRDS(feature.selected,"data/signature.rds")
signature_genes = readRDS("data/signature.rds")

pancancer_list = map(pancancer.names,function(ds_name){
  require(factoextra)
  require(FactoMineR)
  # 1) get ds
  ds_tmp = readRDS(paste0("~/r_workspace/db/tcga/tcga_rds_v2/",ds_name))
  
  # 2) get_clin and expression
  expr = ds_tmp$expr

  clin = ds_tmp$clin %>%
    filter(.$sample %in% colnames(expr)) %>% 
    filter(barcode =="01")# get only primary solid tumor samples
  
  if(nrow(clin) < 100 ){ # remove samples less than 100
    return(NULL)
  }else{
    sig_tmp = 
      func.pca.signature(input.expr = expr,feature.selected = signature_genes) %>% 
      as.data.frame() %>% 
      set_rownames(.[[1]])
    
    clin %<>% 
      mutate(ampk_score = sig_tmp[.$sample,"AMPK_score"])
    return(clin)
    
  }
  
}) %>% 
    set_names(pancancer.names)

pancancer_list
# saveRDS(pancancer_list,"data/pancancer_signature.rds")

# get pancancer 
pancancer_list = readRDS("data/pancancer_signature.rds") %>% 
  {.[lengths(.)!= 0]} %>% 
  map(function(x){
    x %>% 
      fun_surv_parsing(c("OS.time","OS",1)) %>% 
      select(cancer,ampk_score,time,status) %>% 
      mutate(ampk_score = ampk_score /10)
  }) %>% 
  reduce(rbind)

pancancer_list %>% 
  group_by(cancer) %>% 
  do(fun_unicox_multi(.,variable = "ampk_score")) %>% 
  ungroup() %>% 
  mutate(features = cancer) %>% #head
  arrange(hr) %>% #head
  mutate(cancer = factor(cancer,levels = cancer)) %>% #pull(cancer)
  mutate(p = ifelse(pvalue < 0.05,"*","NS")) %>% 
  ggplot(aes(x = hr ,y = cancer))+
  geom_vline(xintercept = 1,color = "gray")+
  geom_point(aes(color = p),shape = 15,size = 2)+
  theme_now()+
  scale_x_log10()+
  ggpubr::color_palette(fun_get_palette(palette)[c(2,1)])

```

# we retrived the immune ds from gse and ICGC ds
```{r}

# luad
signature_genes = readRDS("data/signature.rds")

luad_ds = readRDS("~/r_workspace/db/gse/RDS/LUAD_GSE135222_ICB_pfs.RDS")

luad_clin= func.pca.signature(
  luad_ds$expr,feature.selected = signature_genes
)

luad_ds$clin %>% 
  mutate(ampk_score = luad_clin$AMPK_score[match(rownames(.),luad_clin$Row.names)]) %>% #colnames()
  fun_surv_parsing(c("pfs_time","pfs_status",1)) %>% 
  fun_surv_cutoff(feature = "ampk_score",pct =0.5) %>% 
  fun_surv_km(palette = "lancet",graph_title = "luad_pfs") %>% 
  fun_km_re()

# kirc
kirc_ds = readRDS("~/r_workspace/db/gse/RDS/kirc_icgc_reacEU_os_cancer_normal.rds")

kirc_ds$clin %<>% 
  filter(sample %in% colnames(kirc_ds$expr)) %>% 
  filter(tissue == "cancer")

kirc_clin= func.pca.signature(
  kirc_ds$expr[,kirc_ds$clin$sample],feature.selected = signature_genes
)


kirc_ds$clin %>% 
  mutate(ampk_score = kirc_clin$AMPK_score[match(rownames(.),kirc_clin$Row.names)]) %>% #colnames()
  fun_surv_cutoff(feature = "ampk_score",pct = seq(0.25,0.75,0.01)) %>% 
  fun_surv_km(palette = "lancet",graph_title = "ICGC_KIRC") %>% 
  fun_km_re()

```

# clin table

```{r }
gse13861_clin %>% 
  fun_dt_dt(x_name = "gse13861")
gse26901_clin %>% 
  fun_dt_dt(x_name = "gse26901")

gse66229_clin %>% 
  fun_dt_dt(x_name = "gse66229")

source("~/r_workspace/script/rscript/fun_data_parsing.R")
gse13861_clin %>% 
  mutate(m_stage = paste0("M",M.stage)) %>% 
  fun_data_parsing(features = c("Sex","Age","AJCC6","m_stage"))


tcga_clin_data %>% 
  filter(!is.na(Cluster)) %>% 
  mutate(age = `Diagnosis Age`) %>% 
  mutate(stage = `Neoplasm Disease Stage American Joint Committee on Cancer Code`,
         stage = str_extract(stage,"STAGE I(I|V)*")) %>% 
  fun_data_parsing(
    features = c("age","Sex","T_stage","N_stage","M_stage","stage","grade","Subtype")
  ) ->tmp 

tmp$Char %>% 
  fun_dt_dt()

gse13861_clin %>% 
  mutate(m_stage = paste0("M",M.stage)) %>% 
  fun_data_parsing(features = c("Sex","Age","AJCC6","m_stage","Lauren")) %>% 
  {.[[2]]} %>% 
  fun_dt_dt()

gse26901_clin %>% 
  fun_data_parsing(features = c("Sex","ACRG.sub","AJCC.stage","Lauren","LAUREN 1=intestinal, 2=diffuse, 3=mixed")) %>% 
  {.[[2]]} %>% 
  fun_dt_dt()

gse66229_clin %>% #colnames()
  mutate_all(as.character) %>% 
  fun_data_parsing(c("sex","Lauren","ACRG.sub","T","N","M","Stage"
                     )) %>% 
  {.[[2]]} %>% 
  fun_dt_dt()

```




# other validation

```{r validation}
fun_gse_validation =function(input_ds,nm){
  gse_data = readRDS(input_ds)
  
  clin_now = func.pca.signature(gse_data$expr,
                                   feature.selected = signature_genes) %>% 
  mutate(time = gse_data$clin$time[match(.$Row.names,gse_data$clin$sample)],
         status = gse_data$clin$status[match(.$Row.names,gse_data$clin$sample)])
  
  clin_now %>% 
    fun_surv_cutoff(feature = "AMPK_score",pct = seq(0.25,0.75,0.01)) %>% 
    fun_surv_km(palette = "lancet",graph_title = nm) %>% 
    fun_km_re()
  
}

# BLCA
fun_gse_validation("~/r_workspace/db/gse/RDS/blca_gse32548_os.rds",nm = "BLCA_GSE32548")

# PAAD
fun_gse_validation("~/r_workspace/db/gse/RDS/paad_gse57495_os.RDS",nm = "PAAD_GSE57495")

# LUAD
fun_gse_validation("~/r_workspace/db/gse/RDS/luad_gse13213_os.rds",nm = "LUAD_GSE13213")


```





# tcga suppliment analysis

```{r}
load("../GC_cluster_ampk/.RData")

tcga_clin_data = ds_list$tcga$clin %>% 
  fun_surv_parsing("os")

list(
tcga_clin_data %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "TCGA:OS") ,

tcga_clin_data %>% 
  fun_surv_parsing("dfs") %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "TCGA:DFS") ,

# gse 13861
gse13861_clin %>% 
  mutate(AMPK_score = MAPK_score) %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "GSE13861:OS"),

gse13861_clin %>% 
  mutate(AMPK_score = MAPK_score) %>% 
  fun_surv_parsing(osOrdfs = c("RFS.m","Recurrence (1=yes, 0=no)",1)) %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "GSE13861:RFS") ,

# gse26901
gse26901_clin %>% 
   mutate(AMPK_score = MAPK_score) %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "GSE26901:OS") ,
gse26901_clin %>% #head
   mutate(AMPK_score = MAPK_score) %>% 
  fun_surv_parsing(osOrdfs = c("RFS.m","Recurrence (1=yes, 0=no)",1)) %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "GSE26901:RFS"),



# gse66229
gse66229_clin %>% 
   mutate(AMPK_score = MAPK_score) %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "GSE66229:OS"),

gse66229_clin %>% #head
   mutate(AMPK_score = MAPK_score) %>% 
  fun_surv_parsing(osOrdfs = c("DFS.m","Recur",1)) %>% 
  fun_timeROC(Group = "AMPK_score",data_name = "GSE66229:DFS")) %>% 
  fun_timeROC_merge() -> roc_merge

roc_merge  %>% 
  fun_plot_timeROC_line(group_features = "AMPK_score",ribbon = F)+
  theme(legend.position = "top")

roc_merge$auc %>% 
  mutate(ds = str_remove(data_name,":.+")) %>% 
  mutate(data_name = factor(data_name, levels = unique(data_name))) %>% 
  ggplot(aes(x = data_name,y = auc,fill = factor(time)))+
  geom_bar(stat = "identity",position = "dodge")+
  coord_cartesian(ylim = c(0,0.78))

# 
# fun_clin_surv_strati(
#   tcga_clin_data %>% 
#     mutate(T_stage = str_extr),
#   Risk_score = "AMPK_signature",
#   features = 
# )

```


# nomogram

```{r }
tcga_clin_data%<>% 
  mutate(T_stage = str_extract(`American Joint Committee on Cancer Tumor Stage Code`,"T\\d+"),
         N_stage = str_extract(`Neoplasm Disease Lymph Node Stage American Joint Committee on Cancer Code`,"N\\d+"),
         M_stage = str_extract(`American Joint Committee on Cancer Metastasis Stage Code`,"M\\d+"),
         grade =`Neoplasm Histologic Grade` ) %>% 
  mutate(age =`Diagnosis Age`)

nomo_data = 
  tcga_clin_data %>% 
  mutate(T_stage= ifelse(T_stage %in% c("T1","T2"),"T1-2","T3-4"),
         N_stage = ifelse(N_stage == "N0","N0","N1+")) %>% 
  fun_nomogram(features = c("AMPK_score","Sex","age","T_stage","N_stage","M_stage"),
               B = 1000,m = 100)

```



```{r }

roc_compare = 
  map(c("Points","T_stage","N_stage","M_stage","age","Sex"),function(x){
  print(x)
  nomo_data$data %>% 
    mutate_at(x,fun_data_cha2num) %>% 
    fun_timeROC(Group = x,data_name = x)
  
})  %>% 
  fun_timeROC_merge() 


map(c(1:5)*12,function(x){
  roc_compare %>% 
  fun_plot_timeROC_curve(plot_group = T,
                         group_time = x,
                         palette = get_palette(k=7),
                         legend_suffix = ": ",
                         title = paste0(x/12,"-year survival"))
})

```
